Bandit Multiclass Classification

### 2018-07-18 main.tex

\textbf{Assumption}: If the volume of $\Omega_t$ becomes smaller than $\frac{|\Omega|}{N}$, then the algorithm won't make any error anymore. $N$ should be in the order of $\Theta(\frac{1}{\gamma^{Kd}})$.  \\
\textbf{Rough analysis:} \\
Each time the algorithm makes an error in Line~\ref{line:case1}, the volume becomes $\alpha$ times the original volume. So the algorithm will not make more than $ \frac{\ln N}{\ln \frac{1}{\alpha}} $ mistakes in this case.

@@

@@

\section{One-against-all Perceptron}
Actually, same as Chicheng's writeup's Section 5: Fixed-Threshold Perceptron.

\section{Gradient Descent {\color{red} [TODO]}}
\iffalse
\section{Continuous EXP4 with Uniform Exploration}

\textbf{Discussion.} We can change $\ell_t(\cdot)$ to any reasonable convex loss (e.g., logsitic loss or second-order loss). 
\fi

@@

>>>>

\textbf{Conjecture(should be true)}: If the volume of $\Omega_t$ becomes smaller than $\frac{|\Omega|}{N}$, then the algorithm won't make any error anymore. $N$ should be in the order of $\Theta(\frac{1}{\gamma^{Kd}})$.  \\
\textbf{Rough analysis:} \\
Each time the algorithm makes an error in Line~\ref{line:case1}, the volume becomes $\alpha$ times the original volume. So the algorithm will not make more than $ \frac{\ln N}{\ln \frac{1}{\alpha}} $ mistakes in this case.

@@

\section{How hard it is to use the feedback only from wrong guesses?}
The halving algorithm can actually run if we can do ``uniform sampling'' over the version space. But it is even unknown whether we can efficiently pick a model from the version space. The problem is that we get a lot of feedback in the form of ``feature $x_t$ does not belong to class $\tilde{y}_t$'', which we don't know how to use.

The following is just an attempt (not successful but might be interesting...) to say that it might be not easy to figure out a model if the learner is only presented with this kind of ``error message''.

The problem is formulated as follows. 
Given $N$ points in a row, each one with a class $c_i\in [K]$, $\forall i\in [N]$. We call these $N$ points \textit{separable} if the following statement holds: 
\begin{center}
    If $c_i=c_j$ for some $i\leq j$, then $c_i=c_{i+1}=\cdots=c_j$.
\end{center}
For example, if $N=5, K=3$, then $(c_1,c_2, c_3, c_4,c_5)=(3,3,1,1,1)$ is separable, but $(c_1,c_2,c_3,c_4,c_5)=(2,1,2,2,2)$ is not. 
\ \\
\ \\
Now you have $N$ conditions, in which the $i$-th condition only says something like ``$c_i\neq k$'' for some $k$. \\
(1) Can you efficiently decide whether there exists an assignment of $(c_1,\ldots,c_N)$ such that these $N$ points are separable and satisfy all the conditions? \\
(2) If it is guaranteed that there are separable solutions, can you efficiently find one of them?\\ (Efficient: the complexity is polynomial in $N$ and $K$)
\ \\
\ \\
\textbf{Example 1}. \\
$N=5, K=3$: \\
$c_1\neq 1$ \\
$c_2\neq 2$ \\
$c_3\neq 3$ \\
$c_4\neq 1$ \\
$c_5\neq 2$ \\
$\Rightarrow (c_1,c_2,c_3,c_4,c_5)=(2,1,1,3,3)$ or $(3,3,2,2,1)$ are separable solutions. \\
\ \\
\textbf{Example 2}. \\
$N=7, K=3$: \\
$c_1\neq 1$ \\
$c_2\neq 2$ \\
$c_3\neq 3$ \\
$c_4\neq 1$ \\
$c_5\neq 2$ \\
$c_6\neq 3$ \\
$c_7\neq 1$ \\
$\Rightarrow$ There is no separable solution. \\

It turns out this specific 1-dimensional problem is equivalent to check whether there is a \textbf{missing permutation} of $[K]$ / find a missing permutation in the given subsequence. In example 1, the existed permutations are $(1,2,3), (1,3,2), (2,3,1), (3,1,2)$, the missing ones are $(2,1,3)$ and $(3,2,1)$.  So the solutions can be $(2,1,3)$ or $(3,2,1)$ (with some repetition). In Example 2, all permutations are as subsequences, so there is no solution.

We can prove this equivalence considering two directions: \\
(1) If there is a solution with the class labels following a permutation, then that permutation cannot be a subsequence of the given sequence. \\
(2) If there is a missing permutation in the given sequence, then there is a class assignment that follows this permutation.

@@

\section{One-against-all Perceptron}
Same as Chicheng's writeup's Section 5: Fixed-Threshold Perceptron.

\section{Gradient Descent {\color{red} [TODO]}}

@@

\section{Continuous EXP4 with Uniform Exploration}

\textbf{Discussion.} We can change $\ell_t(\cdot)$ to any reasonable convex loss (e.g., logsitic loss or second-order loss).
